Full-day, in home validation of infant body position measurements from inertial sensors

### 2023-02-17 manuscript.Rmd
overall row

group_agree_cor <- cor_test(agree$group, vars = c("prop_model", "prop_human")) %>% pull(cor)
split_agree_cor <- cor_test(agree$split, vars = c("prop_model", "prop_human")) %>% pull(cor)

@@

```{r, pt2overalltable}
map_dfc(agree, ~ .x %>% group_by(pos) %>% 
          cor_test(vars = c("prop_model", "prop_human")) %>% 
          select(pos, cor))
map_dfc(agree, ~ .x %>% filter(file != "107/3", file != "104/1") %>% group_by(pos) %>% 
          cor_test(vars = c("prop_model", "prop_human")) %>% 
          select(pos, cor))

>>>>

@@

```{r, pt2overalltable}
pt2corr_with_outliers <- map_dfc(agree, ~ .x %>% group_by(pos) %>% cor_test(vars = c("prop_model", "prop_human")) %>% select(pos, cor)) %>% select(-`pos...3`)
pt2corr_without_outliers <- map_dfc(agree, ~ .x %>% filter(file != "107/3", file != "104/1") %>% group_by(pos) %>% cor_test(vars = c("prop_model", "prop_human")) %>% select(pos, cor)) %>% select(-`pos...1`,-`pos...3`)
pt2corr <- bind_cols(pt2corr_with_outliers, pt2corr_without_outliers)
rm(pt2corr_with_outliers)
rm(pt2corr_without_outliers)

#Overall
group_agree_cor <- cor_test(agree$group, vars = c("prop_model", "prop_human")) %>% pull(cor)
split_agree_cor <- cor_test(agree$split, vars = c("prop_model", "prop_human")) %>% pull(cor)
group_agree_cor_noout <- agree$group %>% filter(file != "107/3", file != "104/1") %>% 
  cor_test(vars = c("prop_model", "prop_human")) %>% pull(cor)
split_agree_cor_noout <- agree$split %>% filter(file != "107/3", file != "104/1") %>%
  cor_test(vars = c("prop_model", "prop_human")) %>% pull(cor)
overall_row <- tibble("Overall", group_agree_cor, split_agree_cor, group_agree_cor_noout, split_agree_cor_noout)
colnames(overall_row) <- colnames(pt2corr)
pt2corr <- bind_rows(pt2corr, overall_row)
apa_table(pt2corr, col.names = c("Position", "Group", "Individual", "Group", "Individual"), col_spanners = list(`With Outliers` = c(2, 3), `Without Outliers` = c(4, 5)),
          midrules = 5)
